# Align Associated plots {#aplot}

For many times, we are not just aligning plots as what `cowplot` and `patchwork` did. We would like to align associated information that requires axes to be exactly matched in subplots. 

## A first glance


```{r}
library(ggplot2)
library(aplot)

p <- ggplot(mtcars, aes(mpg, disp)) + geom_point()
p2 <- ggplot(mtcars, aes(mpg)) + 
  geom_density(fill='steelblue', alpha=.5) + 
  ggtree::theme_dendrogram()
p3 <- ggplot(mtcars, aes(x=1, y=disp)) + 
  geom_boxplot(fill='firebrick', alpha=.5) + 
  theme_void()
ap <- p %>% 
  insert_top(p2, height=.3) %>% 
  insert_right(p3, width=.1)
## you can use `ggsave(filename="aplot.png", plot=ap)` to export the plot to image file
print(ap) # or just type ap will print the figure
```

## Aligning plots with a tree


```{r fig.width=7, fig.height=4}
library(ggtree)
set.seed(2020-03-27)
x <- rtree(10)
d <- data.frame(taxa=x$tip.label, value = abs(rnorm(10)))
p <- ggtree(x) + geom_tiplab(align = TRUE) + xlim(NA, 3)

library(ggstance)
p2 <- ggplot(d, aes(value, taxa)) + geom_colh() + 
  scale_x_continuous(expand=c(0,0)) 

library(patchwork)
p | p2
```

Althought `patchwork` did a good job at aligning y-axes among the two plots, the output is not what we want if the bar heights are associated with external nodes on the tree. It is not so obvious for an ordinary user to extract the order of tip label from the tree to re-draw the barplot. 

If we insert a `ggtree` object in `aplot`, it will transform other plots in the same row (`insert_left` and `insert_right`) or same column (`insert_top` and `insert_bottom`) based on the tree structure.


```{r fig.height=4, fig.width=7}
p2 %>% insert_left(p)
```